Morus: Biases in the stream

### 2018-05-09 morusAC_01_Introduction.tex
update overview

\subsubsection*{Paper Outline.}
This paper is organized as follows, we first provide a brief introduction of how Morus operates\ref{sec/Preliminaries}. By showing existance of a certain class of rotational symmetries, we provide with a reduction of Morus namely MiniMorus\ref{sec/introminimorus}. We analysed this simplified scheme in \ref{sec/minitrails}, building a ciphertext-only trail with a weight of 16.
We then extend our result to the full scheme, showing a bias in the keystream over 5 rounds. In \ref{sec/IniFin} we provide new attacks on reduced version of the initialization and the finalization.

>>>>

\subsubsection*{Paper Outline.}
This paper is organized as follows, we first provide a brief introduction of how Morus operates (Sect. \ref{sec/Preliminaries}).
By showing existance of a certain class of rotational symmetries, we provide a reduction of Morus namely MiniMorus (Sect. \ref{sec/introminimorus}).
We analysed this simplified scheme in section \ref{sec/minitrails}, building a ciphertext-only trail with a weight of 16.
We then extend our result to the full scheme, showing a bias in the keystream over 5 rounds (Sec. \ref{sec/fulltrails}).
In section \ref{sec/Discussion} we discuss about the implication of such weakness.
In section \ref{sec/IniFin} we provide new attacks on reduced version of the initialization and the finalization.
